\textcolor{black}{In-silico molecular transport via perivascular networks in the human intracranial space}

### 2025-06-26 paper/main.tex
Work towards complying with journal style.

We represent the evolution and distribution of a solute in the CSF
spaces $\Omega_{\rm CSF}$, brain parenchyma $\Omega_{\rm PAR}$, and
periarterial and perivenous networks $\Lambda_a \cup \Lambda_v$ via a
mixed-dimensional transport model~\cite{masri2024modelling} over a timescale
of minutes to hours (\Cref{fig:results1}A--B, \Cref{fig:csf}A--C). The
current model accounts for solute exchange between the CSF spaces,
brain parenchyma, and the PVSs, diffusion within all compartments,
dispersion and convection in the CSF spaces, and convection within the
PVS. Specifically, for $t > 0$, we solve for a concentration field
$c(x, t)$ in the 3D intracranial compartments (for $x \in \Omega_{\rm
  CSF} \cup \Omega_{\rm PAR}$) and for a cross section-averaged
concentration field $\hat{c}(s, t)$ in the perivascular networks (for
$s \in \Lambda_a, \Lambda_v$) satisfying the following equations:
\begin{subequations}
\begin{alignat}{2}
  \partial_t c - \nabla \cdot D (1 + R) \nabla c  + \nabla \cdot (\bm u_{\rm CSF} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF},
  \label{eq:multi_transport_3d_CSF}
  \\ 
  \partial_t (\phi c) - \nabla \cdot D^{\ast} \nabla (\phi c)  + \nabla \cdot (\bm u_{\rm PAR} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d_PAR}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport_3d_CSF}, $D$ is the (free) diffusion
coefficient of the solute, $R$ is the dispersion coefficient in the
CSF spaces, $\bm u_{\rm CSF}$ is the steady CSF velocity, $\xi$ is a
permeability allowing for transfer/exchange across the interfaces
$\Gamma_a, \Gamma_v$ between the periarterial and perivenous networks
and their surroundings, the overlined $\overline{c}$ denotes the
average of $c$ over cross-sections of $\Gamma_a, \Gamma_v$, and
$\delta_{\Gamma}$ is a Dirac term concentrated on $\Gamma_a,
\Gamma_v$. Additionally, in \eqref{eq:multi_transport_3d_PAR}, $\phi = \phi_{\rm ECS}$
is the brain extracellular volume fraction\footnote{We set $\phi =
1.0$ in $\Omega_{\rm CSF}$ and therefore omit $\phi$
in~\eqref{eq:multi_transport_3d_CSF}.}, $D^{\ast}$ is the effective
diffusion coefficient in the parenchyma, and $\bm u_{\rm PAR}$ is an
interstitial fluid velocity. In this study, we set $\bm u_{\rm PAR} =
0$. In~\eqref{eq:multi_transport_1d}, $A = \pi (R_2^2 - R_1^2)$ is the
area and $P = 2 \pi R_2$ is the perimeter of the PVS cross-sections,
$\hat{D}$ is the effective diffusion coefficient in the PVSs, and
$\hat{u}$ is the fluid velocity (in the axial direction) in the PVS
defined for the periarterial and perivenous spaces separately
($\hat{u}|_{\Lambda_a} = \hat{u}_a$, $\hat{u}|_{\Lambda_v} =
\hat{u}_v$). Further, we model the membrane between the parenchyma and
the CSF spaces as a semi-permeable membrane with permeability
coefficient $\beta_{\rm pia}$, allowing for a jump in $c$ there. The
initial concentrations in $\Omega$ and networks $\Lambda_a, \Lambda_v$
are all set to zero.

@@

>>>>

We represent the evolution and distribution of a solute in the CSF
spaces $\Omega_{\rm CSF}$, brain parenchyma $\Omega_{\rm PAR}$, and
periarterial and perivenous networks $\Lambda_a \cup \Lambda_v$ via a
mixed-dimensional transport model~\cite{masri2024modelling} over a timescale
of minutes to hours (\Cref{fig:results1}A--B, \Cref{fig:csf}A--C). The
current model accounts for solute exchange between the CSF spaces,
brain parenchyma, and the PVSs, diffusion within all compartments,
dispersion and convection in the CSF spaces, and convection within the
PVS. Specifically, for $t > 0$, we solve for a concentration field
$c(x, t)$ in the 3D intracranial compartments (for $x \in \Omega_{\rm
  CSF} \cup \Omega_{\rm PAR}$) and for a cross section-averaged
concentration field $\hat{c}(s, t)$ in the perivascular networks (for
$s \in \Lambda_a, \Lambda_v$) satisfying the following equations:
\begin{subequations}
\begin{alignat}{2}
  \partial_t c - \nabla \cdot D (1 + R) \nabla c  + \nabla \cdot (\bm u_{\rm CSF} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF},
  \label{eq:multi_transport_3d_CSF}
  \\ 
  \partial_t (\phi c) - \nabla \cdot D^{\ast} \nabla (\phi c)  + \nabla \cdot (\bm u_{\rm PAR} c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d_PAR}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport_3d_CSF}, $D$ is the (free) diffusion
coefficient of the solute, $R$ is the dispersion coefficient in the
CSF spaces, $\bm u_{\rm CSF}$ is the steady CSF velocity, $\xi$ is a
permeability allowing for transfer/exchange across the interfaces
$\Gamma_a, \Gamma_v$ between the periarterial and perivenous networks
and their surroundings, the overlined $\overline{c}$ denotes the
average of $c$ over cross-sections of $\Gamma_a, \Gamma_v$, and
$\delta_{\Gamma}$ is a Dirac term concentrated on $\Gamma_a,
\Gamma_v$. Additionally, in \eqref{eq:multi_transport_3d_PAR}, $\phi = \phi_{\rm ECS}$
is the brain extracellular volume fraction, $D^{\ast}$ is the effective
diffusion coefficient in the parenchyma, and $\bm u_{\rm PAR}$ is an
interstitial fluid velocity. In this study, we set $\bm u_{\rm PAR} =
0$. In~\eqref{eq:multi_transport_1d}, $A = \pi (R_2^2 - R_1^2)$ is the
area and $P = 2 \pi R_2$ is the perimeter of the PVS cross-sections,
$\hat{D}$ is the effective diffusion coefficient in the PVSs, and
$\hat{u}$ is the fluid velocity (in the axial direction) in the PVS
defined for the periarterial and perivenous spaces separately
($\hat{u}|_{\Lambda_a} = \hat{u}_a$, $\hat{u}|_{\Lambda_v} =
\hat{u}_v$). Further, we model the membrane between the parenchyma and
the CSF spaces as a semi-permeable membrane with permeability
coefficient $\beta_{\rm pia}$, allowing for a jump in $c$ there. The
initial concentrations in $\Omega$ and networks $\Lambda_a, \Lambda_v$
are all set to zero.

@@

Numerical simulation results generated as part of this study are
openly available on Zenodo with the identifier doi:
10.5281/zenodo.14749163. This archive includes surface triangulations
used for geometry representation, computational meshes (3D meshes and
1D networks), segmentations, sample simulation outputs from the
baseline and high PVS flow models, and animations.

\section*{Code availability}
